---
title: "Alcohol vs Seat choice"
author: "Eduardo Noriega"
date: "Sept. 14, 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??
 
## Now with ggplot - first select the basic data
##methods
Seat is a categorical variable.
Alcohol is a numerical variable.
For this problem we explain alcohol consumption, based on where people sit.  
Therefore the helper file is Numerical, categorical.  

$H_0$: There is no difference between the average number of drinks imbibed between people conditioned on the row they sit in. 

$H_A$: The average number drinks is different between at least two rows.
```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys 

## Inferential Tests

## Conclusions


